Isotope data reduction

### 2020-12-10 isotope_data_reduction.rmd
no update

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(readxl)
```

>>>>

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia)
library(readxl)
```
